Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
More changes and more comments

There is, then, space for other EC frameworks that do not make any of
these assumptions, such as {\sf NodIO} presented in
\cite{2016arXiv160101607Manom}. {\sf NodIO} implements the server of a % (Paloma) Only the server?
client/server application and has some support to program an
evolutionary algorithm embedded in pages served by them which can then
communicate between each other via that server. The client part can run in any
web-enabled device, including many over which developers have no
control, that is, volunteers.

@@

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer computing frameworks written in compiled languages,
such as C++ or Java, that, in principle, can achieve better performance than
JavaScript. However, one of the advantages of our architecture is that
clients do not need to install anything on their machines, they just
%Pablo: According English Stack Exchange, you install "ON" a machine (but "IN" a directory)
need to open a web page  
in a compatible, that is, almost any, browser, such as Chrome, Safari or  Firefox, which are
available in almost every desktop or mobile device. Another advantage is
that the source code can be directly examined by volunteers, because it is not
compiled as other options such as Java Applets, ActionScript or
ActiveX are. Also, as we will discuss in this paper, it can provide some extra
features such as enhanced security or operating system
independence. This system, however, is not intended to substitute
already existing frameworks running on dedicated hardware or the cloud, but to
%Pablo: same here, I learnt this with my paper of EAs "on clusters"
complement them.

@@

%Mario: Rewrote: 
%One of the aspects that must be taken into account in volunteer based
%frameworks is its {\em social} aspect in the design, with 
In general, several volunteers will be needed to
overcome the overhead involved in using a client-server architecture
and this number of volunteers is obviously not guaranteed. Therefore, the {\em social} aspect must be taken into account when designing 
volunteer based frameworks, with 
issues related to security, trust, and privacy among others. 
The computing system becomes then a {\em techno-social system}
\cite{vespignani2009predicting}. In that sense, its social aspects
cannot be separated from its technical specifications, with one
feeding into the other. One of these aspects is safety for the user
and the scientist running it: the user must be reasonably sure that the
experiment is not misusing its resources and the scientist must have a
certain safety in the sense that its server is not going to be
attacked via cheating or denial of service attacks. We have decided to
approach this in a pragmatic way. Including many security features
would decrease performance; on the other hand, we publish all data
resulting from the experiment once private information, such as IPs,
has been processed to an untraceable hash. The experiments themselves
are a proof that there are enough users trusting the experiment to
give it its CPU time and that there has been no attempt to cheat by
sending specially crafted chromosomes or to attack the server to make
it stop working because there was no incentive in doing so. The
system, besides, is running in a dedicated Platform as a Service (PaaS)
container or Virtual Private Server so accessing the server would only
show the few data obtained from the experiment, nothing more. Making it
free software ensured this was known by anyone in the experiment, via
links in the web page that hosted it.

>>>>

There is, then, space for other EC frameworks that do not make any of
these assumptions, such as {\sf NodIO} presented in
\cite{2016arXiv160101607Manom}. {\sf NodIO} implements a client-server application; the server offers the possibility to program an
evolutionary algorithm that is embedded in the served pages, and those pages can communicate between each other via the server. On the other hand, the client part can run in any
web-enabled device, including many over which developers have no
control, that is, volunteers.

@@

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer computing frameworks written in compiled languages,
such as C++ or Java, that, in principle, can achieve better performance than
JavaScript. However, one of the advantages of {\sf NodIO} architecture is that
clients do not need to install anything on their machines, they just
%Pablo: According English Stack Exchange, you install "ON" a machine (but "IN" a directory)
need to open a web page  
in a compatible, that is, almost any, browser, such as Chrome, Safari or  Firefox, which are
available in almost every desktop or mobile device. Another advantage is
that the source code can be directly examined by volunteers, because it is not
compiled as other options such as Java Applets, ActionScript, or
ActiveX are. Also, as we will discuss in this paper, it can provide some extra
features such as enhanced security or operating system
independence. This system, however, is not intended to substitute
already existing frameworks running on dedicated hardware or the cloud, but to
%Pablo: same here, I learnt this with my paper of EAs "on clusters"
complement them.

@@

%Mario: Rewrote: 
%One of the aspects that must be taken into account in volunteer based
%frameworks is its {\em social} aspect in the design, with 
In general, several volunteers will be needed to
overcome the overhead involved in using a client-server architecture
and this number of volunteers is obviously not guaranteed. Therefore, the {\em social} aspect must be taken into account when designing 
volunteer based frameworks, with 
issues related to security, trust, and privacy among others. 
The computing system becomes then a {\em techno-social system}
\cite{vespignani2009predicting}, in the sense that its social aspects
cannot be separated from its technical specifications, with one
feeding into the other. One of these aspects is safety for the user running it, as well as for the scientist: the user must be reasonably sure that the
experiment is not misusing their resources and the scientist must have a
certain safety in the sense that their server is not going to be
attacked via cheating or denial of service attacks. We have decided to
approach this in a pragmatic way. Including many security features % (Paloma) I'm kind of lost here... Sentences seem to be unconnected and unrelated...
would decrease performance; on the other hand, we publish all data
resulting from the experiment once private information, such as IPs,
has been processed to an untraceable hash. The experiments themselves
are a proof that there are enough users trusting the experiment to
give it its CPU time and that there has been no attempt to cheat by
sending specially crafted chromosomes or to attack the server to make
it stop working because there was no incentive in doing so. The
system, besides, is running in a dedicated Platform as a Service (PaaS)
container or Virtual Private Server so accessing the server would only
show the few data obtained from the experiment, nothing more. Making it
free software ensured this was known by anyone in the experiment, via
links in the web page that hosted it.
